Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
Added figure on engagement level
Diego Results
need to count demo-letters

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{engagement}
    \caption{Engagement level of the child, manually annotated by two judges
        over the 13 min long interaction (Cronbach’s alpha test: $\alpha = .82$,
        good inter-judge agreement). The vertical lines represent activity
    switches between handwriting teaching and story-telling (used as a
    distruber).}
    \label{}
\end{figure}

@@

\subsubsection{Results}
Diego completly accepted our scenario and seriously played the game. At the
begining he seemed not confident and intimidated.  But quickly, he gain in
confidence and complicity with the robot. Finally, he showed a real affinity, so
that he sent an handwrited mail to it some days after the last
session.\\

In all sessions, Diego was fully focused on the activity during forty minutes up to one
hour. In total, he provided X letters as demonstration.\\

Diego felt he improved the robot's handwriting. To make clearly visible this
improvement, we printed the letter that the robot writted during the third
session before and after the help of diego~\ref{fig:stimuli}.
